%%%%%%%%%%%%%%%%%
% This is an sample CV template created using altacv.cls
% (v1.1.2, 1 February 2017) written by LianTze Lim (liantze@gmail.com). Now compiles with pdfLaTeX, XeLaTeX and LuaLaTeX.
% 
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

%% If you need to pass whatever options to xcolor
\PassOptionsToPackage{dvipsnames}{xcolor}

%% If you are using \orcid or academicons
%% icons, make sure you have the academicons 
%% option here, and compile with XeLaTeX
%% or LuaLaTeX.
% \documentclass[10pt,a4paper,academicons]{altacv}
\documentclass[10pt,a4paper]{altacv}

%% AltaCV uses the fontawesome and academicon fonts
%% and packages. 
%% See texdoc.net/pkg/fontawecome and http://texdoc.net/pkg/academicons for full list of symbols.
%% 
%% Compile with LuaLaTeX for best results. If you
%% want to use XeLaTeX, you may need to install
%% Academicons.ttf in your operating system's font 
%% folder.


% Change the page layout if you need to
\geometry{left=1cm,right=9cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=1.25cm,bottom=1.25cm}

% Change the font if you want to.

% If using pdflatex:
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[default]{lato}
\usepackage{multicol}

% If using xelatex or lualatex:
% \setmainfont{Lato}

% Change the colours if you want to
\definecolor{Mulberry}{HTML}{40423f}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{heading}{Mulberry}
\colorlet{accent}{Mulberry}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}
\newcommand{\sbt}{\,\begin{picture}(-1,1)(-1,-3)\circle*{3}\end{picture}\ \hspace{0.5em}}

\begin{document}
\name{Jon Barber}
\tagline{Learn, build, break, repeat.}

% \photo{2.8cm}{Globe_High}

\personalinfo{%
  % Not all of these are required!
  % You can add your own with \printinfo{symbol}{detail}
  \email{JonBarberEmail@gmail.com}
  \phone{607-267-6408}
  \mailaddress{1545 NW Market St \#718}
  \location{Seattle, WA}
  \homepage{bonjarber.com/}
  \twitter{@bonjarber}
  \linkedin{linkedin.com/in/jon-barber-security}
  \github{github.com/bonjarber}
  %% You MUST add the academicons option to \documentclass, then compile with LuaLaTeX or XeLaTeX, if you want to use \orcid or other academicons commands.
%   \orcid{orcid.org/0000-0000-0000-0000}
}

\begin{adjustwidth}{}{-8cm}
\makecvheader
\end{adjustwidth}

% --------------------------------------------------------------------------- %
\cvsection[page1sidebar]{Experience}
% --------------------------------------------------------------------------- %

% -------------- %
\cvjob{Senior Security Consultant}{NCC Group}{(Formerly iSEC Partners)}{February 2015 -- Ongoing}{Seattle, WA}
% -------------- %
\cvtask{Engaged in penetration tests for US tech. industry clients.}
\cvtask{Rapidly learned new systems, stacks, and technologies.}
\cvtask{Found vulnerabilities in web apps, mobile apps, networks, network devices, architecture designs, and source code.}
\cvtask{Created detailed vulnerability reports explaining the engagement and each finding in a way useful to engineers but relevant to executives.}
\cvtask{Tech lead over 75\% of engagements and directly managed consultants.}
\cvtask{Performed self directed research that resulted in a conference talk.}
\cvtask{Organized Security Open Forums at Oculus and Tableau.}
\cvtask{Hosted over 15 Fauxpen Forums, Poker Nights, and Game Nights.}

\divider

% -------------- %
\cvjob{Penetration Tester}{Rhino Security Labs}{Contract Work}{December 2014 -- January 2015}{Remote}
% -------------- %
\cvtask{Performed contract-based, self directed web application pentesting and social engineering.}
\cvtask{Delivered custom written reports detailing vulnerability locations, risks, and recommendations.}

\divider

% -------------- %
\cvjob{Security Engineer}{FactSet}{Internship and Part Time}{June 2014 -- December 2014}{Norwalk, CT / Remote}
% -------------- %
\cvtask{Identified vulnerabilities and managed the remediation of them in FactSet systems, applications, and products.}
\cvtask{Performed threat modeling, wrote security policies, and provided developer security training.}

% --------------------------------------------------------------------------- %
\cvsection{Projects}
% --------------------------------------------------------------------------- %

% -------------- %
\cvproject{Wireless Elephant in the Room}{October 2016}{Toorcon San Diego}
% -------------- %
Found zero days in 20 common off the shelf home routers including Internet-based command injection, auth bypass, ISP backdoor, and more.

\divider

% -------------- %
\cvproject{SAMLyze}{August 2015}{Black Hat USA - Arsenal}
% -------------- %
Acts as an rogue IdP to perform attacks against SAML Service Providers.

\divider

% -------------- %
\cvproject{Covert and Persistent Twitter Botnet}{December 2015}{RIT}
% -------------- %
Developed a proof of concept that used crypto, stego, and hashtags to
maintain an extremely resilient and hard to detect botnet over Twitter.

\medskip

\end{document}
